Viral Sequence Sorting Tools Evaluation

### 2022-11-21 EnvironmentalData/identifying_viral_contigs_environmental.Rmd
Updating figures summarizing testing data.

```{r}
# dataset name for file organization and outputs for metrics file
dataset_name <- "drinking_water" #replace with the dataset_name from "building_env_data_viral_features_set.Rmd"
#name from building_env_data_viral_features_set.Rmd
viruses_filename <- 'merged_viral_feature_outputs.csv'

viruses <- read_tsv(paste(dataset_name, viruses_filename, sep='_'))
```

>>>>

```{r}
# dataset name for file organization and outputs for metrics file
dataset_name <- "drinking_water" #replace with the dataset_name from "building_env_data_viral_features_set.Rmd"
#name from building_env_data_viral_features_set.Rmd
viruses_filename <- 'merged_viral_feature_outputs_nluk.csv'

viruses <- read_tsv(viruses_filename)
```

### 2022-11-21 TestingPipeline/Scripts/rule_tuning_2022.09.06.Rmd
Updating figures summarizing testing data.

@@

>>>>

```{r}
viruses$true_virus <- "not"
viruses$true_virus[viruses$seqtype=="virus"] <- "virus"

viruses_long_scores <- viruses %>% 
  select(contains("keep_score_vb"), size_class, true_virus) %>%
  pivot_longer(cols=contains("keep_score_"), 
               names_to="rule_combination",
               values_to="viral_score") %>% 
  mutate(viral_score=as.factor(round(viral_score))) %>%
  group_by(rule_combination, viral_score, size_class, true_virus) %>%
  summarise(n = n())

viruses_long_scores$size_class <- factor(viruses_long_scores$size_class,
                                    levels = c("3-5kb", "5-10kb", ">10kb"))
```

```{r}
ggplot(viruses_long_scores, aes(y=n, x=rule_combination,
                   fill=viral_score)) +
  geom_bar(stat="identity") +
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    legend.position = "bottom"
  ) +
  scale_fill_brewer(palette = "PuOr", ) +
  xlab("") +
  ylab("Number of Sequences") + 
  facet_grid(~true_virus, scales = "free")
```

```{r}
ggplot(viruses_long_scores, aes(y=n, x=rule_combination,
                   fill=viral_score)) +
  geom_bar(stat="identity") +
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    legend.position = "bottom"
  ) +
  scale_fill_brewer(palette = "PuOr", ) +
  xlab("") +
  ylab("Number of Sequences") + 
  facet_grid(size_class~true_virus, scales = "free")
```

@@

## another way of visualizing the different tool sets scores
```{r}
viruses$true_virus <- "not"
viruses$true_virus[viruses$seqtype=="virus"] <- "virus"

viruses_long_scores <- viruses %>% 
  select(contains("keep_score_high"), contains("keep_score_all"), size_class, true_virus) %>%
  pivot_longer(cols=contains("keep_score_"), 
               names_to="rule_combination",
               values_to="viral_score") %>% 
  mutate(viral_score=as.factor(round(viral_score))) %>%
  group_by(rule_combination, viral_score, size_class, true_virus) %>%
  summarise(n = n())

viruses_long_scores$size_class <- factor(viruses_long_scores$size_class,
                                    levels = c("3-5kb", "5-10kb", ">10kb"))
```

```{r}
ggplot(viruses_long_scores, aes(y=n, x=rule_combination,
                   fill=viral_score)) +
  geom_bar(stat="identity") +
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    legend.position = "bottom"
  ) +
  scale_fill_brewer(palette = "PuOr", ) +
  xlab("") +
  ylab("Number of Sequences") + 
  facet_grid(~true_virus, scales = "free")
```

```{r}
ggplot(viruses_long_scores, aes(y=n, x=rule_combination,
                   fill=viral_score)) +
  geom_bar(stat="identity") +
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    legend.position = "bottom"
  ) +
  scale_fill_brewer(palette = "PuOr", ) +
  xlab("") +
  ylab("Number of Sequences") + 
  facet_grid(size_class~true_virus, scales = "free")
```
